M-M paper, morphological bias

### 2015-03-27 papers/MbhMsph/mm.tex
fri

\section{Data}
\label{sec:data}
Our galaxy sample consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
at the time we started this project, 
and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
Bulge luminosities were derived from our state-of-the-art galaxy decompositions, which take into account 
bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
Kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} was used 
to confirm the presence of rotationally supported components in most early-type galaxies, 
and to identify their extent (intermediate-scale, embedded disks or large-scale disks). 
\emph{Paper I} will present the dataset used here to investigate the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
and illustrate the individual 66 galaxy decompositions.

@@

>>>>

\section{Data}
\label{sec:data}
Our galaxy sample consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
\citep{grahamscott2013,rusli2013bhmassesDM} at the time we started this project, 
and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
Bulge luminosities were derived from our state-of-the-art galaxy decompositions, which take into account 
bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
Kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} was used 
to confirm the presence of rotationally supported components in most early-type galaxies, 
and to identify their extent (intermediate-scale, embedded disks or large-scale disks). 
\emph{Paper I} will present the dataset used here to investigate the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
discuss how we estimated the uncertainties on the bulge parameters, 
and illustrate the individual 66 galaxy decompositions. \\
Bulge luminosities\footnote{Absolute luminosities were calculated assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$ \citep{sani2011}.} 
were converted into stellar masses using the colour-$\Gamma_{3.6}$ relation published by 
\citeauthor{meidt2014} (\citeyear{meidt2014}, their equation 4), 
which allows one to estimate the $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6}$, of a galaxy 
from its $[3.6] - [4.5]$ colour. 
Individual $[3.6] - [4.5]$ colours\footnote{These are integrated $[3.6] - [4.5]$ colours, measured in a circular aperture 
within one galaxy's effective radius.} were taken from 
\citeauthor{peletier2012} (\citeyear{peletier2012}, column 8 of their Table 1) 
when available for our galaxies, 
or were estimated from the bulge stellar velocity dispersion, $\sigma$, 
using the colour-$\sigma$ relation presented by \citeauthor{peletier2012} (\citeyear{peletier2012}, their Figure 6).
We point out here that using a single $\Gamma_{3.6} = 0.6$, independent of $[3.6] - [4.5]$ colour, 
does not significantly affect the results of our analysis.

\input{table_sample.tex}

@@

\section{Analysis}
\label{sec:anal}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
\caption{}
\label{fig:}
\end{center}
\end{figure}
